---
title: "P8105 Homework 5 [td2704]"
output: github_document
---


```{r, echo=FALSE, message=FALSE}

library(tidyverse)
library(dplyr)

```

## Problem 1

```{r}

homicide_data = read_csv("data/homicide-data.csv", na = c("", "Unknown"))
homicide_data
```

The raw homicide data has `r nrow(homicide_data)` rows and `r length(colnames(homicide_data))` columns with variables `r colnames(homicide_data)`. 


```{r}

homicide_data_modified = 
  homicide_data %>%
  mutate(
    city_state = paste(city,state,sep = ", ")
  )
homicide_data_modified
```

```{r}
homicide_counts_df = 
  homicide_data_modified %>%
  group_by(city_state, disposition) %>%
  summarise(
    homicides_by_disposition = n()
  ) %>%
  group_by(city_state) %>%
  mutate(
    total_num_homicides = sum(homicides_by_disposition)
  ) %>%
  filter(disposition == "Closed without arrest" | disposition == "Open/No arrest") %>%
  group_by(city_state) %>%
  mutate(
    num_unsolved_homicides = sum(homicides_by_disposition)
  ) %>%
  select(city_state, total_num_homicides, num_unsolved_homicides) %>%
  distinct(city_state, total_num_homicides, num_unsolved_homicides)

homicide_counts_df
```

For Baltimore, MD: 
```{r}
baltimore_data = 
  homicide_counts_df %>%
  filter(city_state == "Baltimore, MD")

baltimore_prop_test = 
  prop.test(
    x = pull(baltimore_data, num_unsolved_homicides),
    n = pull(baltimore_data, total_num_homicides)
    )

baltimore_prop_test

baltimore_prop_test %>%
  broom::tidy() %>%
  select(estimate, conf.low, conf.high)
  
```
Let's make what we did for Baltimore, MD into a function so that we can apply this across all cities in our df.

```{r}

prop_test_city_function = function(city) {
  city_data = 
    homicide_counts_df %>%
    filter(city_state == city)
  
  city_prop_test = 
    prop.test(
      x = pull(city_data, num_unsolved_homicides),
      n = pull(city_data, total_num_homicides)
    )
  
  return(city_prop_test)
}

```

Apply this function to all cities in homicide_counts_df.
```{r}

test_on_all_cities_df = 
  homicide_counts_df %>%
  mutate(
    test_results = map(city_state, prop_test_city_function),
    tidy_results = map(test_results, broom::tidy)
  ) %>%
  select(city_state, tidy_results) %>%
  unnest(tidy_results) %>%
  select(city_state, estimate, conf.low, conf.high)

test_on_all_cities_df

```

Now that we have our proportion estimates and CIs for each city, let's plot them. 

```{r}
test_on_all_cities_df %>%
  ggplot(aes(x=fct_reorder(city_state, desc(estimate)), y=estimate)) +
  geom_point() +
  geom_errorbar(aes(ymin=conf.low,ymax=conf.high)) +
  theme(axis.text.x = element_text(angle=90, vjust = 0.5, hjust = 1)) +
  xlab("City, State") +
  ylab("Proportion estimate") +
  ggtitle("Proportion of unsolved homicides by city")
```

## Problem 2

Let's take a look at data from this longitudinal study.

```{r, message=FALSE}

experiment_df = 
  tibble(
    files = list.files("data/zip_data/")
    ) %>%
  mutate(
    read_data = purrr::map(str_c("data/zip_data/",files),read_csv)
  ) %>%
  unnest(cols = read_data) %>%
  mutate(
    subject = substr(files,1,6),
    arm = substr(files,1,3)
  ) %>%
  relocate(subject, arm)

experiment_df

```

Now let's create a spaghetti plot showing observations on each subject over time.

```{r}
experiment_df %>%
  pivot_longer(
    week_1:week_8,
    names_to = "week_number",
    values_to = "observations"
  ) %>%
  ggplot(aes(x=week_number,y=observations)) +
  geom_line(aes(group=subject,color=arm)) +
  ggtitle("Observations over weeks for subjects from control and experimental arm")
```

As we can see by the spaghetti plots above, grouped by control and experimental arms, the observations for subjects from the experimental arm increased over the weeks while it seems as though observations for subjects from the control arm stay roughly the same over time. There is some variability among subjects in both of the arms of the study, but overall, we notice an increasing trend over time for the experimental arm and fairly flat trend for the control arm.


## Problem 3

First, we introduce NA values to the dataset.

```{r}

set.seed(10)

iris_with_missing = iris %>% 
  map_df(~replace(.x, sample(1:150, 20), NA)) %>%
  mutate(Species = as.character(Species))

iris_with_missing
```

Now we create a function to fill in these missing values based on numeric or character vector.

```{r}
fill_in_missing = function(vector) {
  if (is.numeric(vector)) {
    mean_vec = mean(vector, na.rm = TRUE)
    vector = replace_na(vector,mean_vec)
  }
  if (is.character(vector)) {
    vector = replace_na(vector,"virginica")
  }
  return(vector)
}

```

Apply this function to each column of the dataframe.

```{r}
iris_fill_in_missing = 
  iris_with_missing %>%
  map_df(fill_in_missing)

iris_fill_in_missing

sum(is.na(iris_with_missing))
sum(is.na(iris_fill_in_missing)) # check that all na values were successfully  replaced
mean(pull(iris_with_missing,Sepal.Length),na.rm = TRUE) # check that correct value was replaced
```




